Probabilistic Inference of NYC Congestion from Taxi Data

### 2017-12-09 reports/paper/paper.tex

\begin{itemize}
\item What are the exact details of the dataset that you used? (Number of data points / standard or non-standard / synthetic or real / exact form of the data)

@@

\item What are the exact details of the metric used?
\end{itemize}

>>>>

{
\color{gray}
\begin{itemize}
\item What are the exact details of the dataset that you used? (Number of data points / standard or non-standard / synthetic or real / exact form of the data)

@@

\item What are the exact details of the metric used?
\end{itemize}
}

For our dataset, we started with the TLC dataset of all NYC taxi trips taken in
January 2009. From the raw data, several computed columns were added.
One-hot-encoded columns were added for hour of day (24 columns) as well as for
day of the week (7 columns). The duration of the trip was also explicitly
computed in seconds as the dependent variable to predict.

In addition to adding columns, the original dataset was filtered. Geographic
coordinates were\ldots
